Certified Knowledge Compilation \\ with Application to Verified Model Counting

### 2023-03-20 doc/mc-paper.tex
Minor changes to appendix

A single recursive step of $\validate$ can encounter product nodes
having many literals as children.  The naive formulation of $\validate$
considers each literal $\lit \in L$ separately.
Literal grouping allows all literals to be validated with a single call to a SAT solver.
It collects those literals
$\lit_1, \lit_2, \ldots, \lit_m$ that cannot be validated by BCP and defines a
product node $\nodev$ having these literals as children.  The goal
then becomes to prove that any total assignment must yield 1 for extension
variable $v$.  A single call to the solver can generate this proof by invoking it on the formula
  $\simplify{\psi}{\passign} \cup \simplify{\theta_{\nodev}}{\{ \obar{v} \}}$ to show that is unsatisfiable.
  The proof steps can be mapped back into clause addition steps in the CRAT file, using as hints the
  input clauses and the defining clauses for $\nodev$.

@@

The proof generator can exploit the sharing of subgraphs
by constructing and proving a {\em lemma} for each node
$\nodeu$ having $\indegree(\nodeu) > 1$.  This proof shows that any
total assignment $\assign$ that satisfies formula $\gamma_{\nodeu}$ must yield
$\assign(u) = 1$.  This lemma is then invoked for every node having
$\nodeu$ as a child.
As a result, the generator will make recursive calls during a call to $\validate$ only once for each node in the POG\@.

>>>>

A single recursive step of $\validate$ can encounter product nodes
having many literals as children.  The naive formulation of $\validate$
considers each literal $\lit \in L$ separately.
Literal grouping allows all literals to be validated with a single call to a SAT solver.
It collects those literals
$\lit_1, \lit_2, \ldots, \lit_m$ that cannot be validated by BCP and defines a
product node $\nodev$ having these literals as children.  The goal
then becomes to prove that any total assignment must yield 1 for extension
variable $v$.  A single call to the solver can generate this proof by invoking it on the formula
  $\simplify{\psi}{\passign} \cup \simplify{\theta_{v}}{\{ \obar{v} \}}$, which should be unsatisfiable.
  The proof steps can be mapped back into clause addition steps in the CRAT file, incorporating the 
  input clauses and the defining clauses for $\nodev$ into the hints.

@@

The proof generator can exploit the sharing of subgraphs
by constructing and proving a {\em lemma} for each node
$\nodeu$ having $\indegree(\nodeu) > 1$.  This proof shows that any
total assignment $\assign$ that satisfies formula $\gamma_{\nodeu}$ and the defining clauses for the POG must yield
$\assign(u) = 1$.  This lemma is then invoked for every node having
$\nodeu$ as a child.
As a result, the generator will make recursive calls during a call to $\validate$ only once for each node in the POG\@.
